A hazards approach to the biometric analysis of infant mortality

### 2023-04-02 Slides/slides.Rmd
add normal time

##

@@

*   Good

>>>>

## Skellefteå 1801--1820

@@

*   Advantages of the hazards method.
       *    Fits naturally into modern survival analysis, allows censored and truncated data, and 
       *   The exogenous component forms a class of proportional hazards distributions.

*   Restriction for both models.
    *   Models for populations, not for individuals.
    *   Less useful for traditional survival analysis.
    *.  The log-cube transform is not universal.
